---
title: "data examples"
author: "nik@nikhouri.com"
output:
  html_document:
    fig_width: 10
    fig_height: 6
    toc: TRUE
    css: style.css
---

# Reading Data

## Import from CSV

Specifying column types saves import time and additional steps later--especially when dates/times are involved.

```{r}
# Read in data file to data frame
df <- read.csv('data/ufwdata.csv', sep=';',
               colClasses=c("POSIXct","character","character"))

str(df)
```

## Inline data

Useful for keeping things to one file (for small data sets). Paste data into a string and read it as if it's a CSV.

```{r}
# Specify data in a string
data <- '"time";"country";"service"
2020-09-14 06:00:00;"Germany";"9545 (NA)"
2020-09-14 06:00:00;"UK";"9703 (NA)"
2020-09-14 06:00:00;"China";"13579 (NA)"
2020-09-14 06:00:00;"Russia";"11684 (NA)"
2020-09-14 06:00:00;"Germany";"11988 (NA)"
2020-09-14 06:00:00;"China";"1433 (ms-sql-s)"
2020-09-14 06:00:00;"Russia";"3694 (NA)"
2020-09-14 06:00:00;"Germany";"17805 (NA)"
2020-09-14 06:00:00;"Netherlands";"36350 (NA)"'

# Read data from the string
df <- read.csv(text=data, sep=';',
               colClasses=c("POSIXct","character","character"))

str(df)
```

# External Data Sources

## Quandl

Free data from Quandl doesn't need an account (for now)

```{r}
library(Quandl)

# Initialize data series & data set identifiers
oildata <- NULL
oilsets <- list("Kuwait" = "BP/OIL_PROD_D_KWT",
                "Oman" = "BP/OIL_PROD_D_OMN",
                "UAE" = "BP/OIL_PROD_D_ARE",
                "Saudi Arabia" = "BP/OIL_PROD_D_SAU",             
                "Qatar" = "BP/OIL_PROD_D_QAT",
                "Iran" = "BP/OIL_PROD_D_IRN")

# Download time series for each country
for (country in names(oilsets)) {
    data <- Quandl(as.character(oilsets[country]))
    data$Country <- country
    oildata <- rbind(oildata,data)
}

head(oildata)
summary(oildata)

#write.table(oildata,file="data/oildata.csv", sep=";", row.names=FALSE)
```

# Summaries

## `topn()`

Show a count, percent, and cumulative percent of items in a list

```{r}
# Read in data file to data frame
df <- read.csv('data/ufwdata.csv', sep=';',
               colClasses=c("POSIXct","character","character"))

# Summarise count, pct, cmlpct for Top N items of list x. n=Inf shows everything
topn <- function(x, label="x", n=25) {
    tab <- table(x, dnn=label) # Count of each element
    df <- as.data.frame(tab, stringsAsFactors=FALSE) # Dataframe of list counts
    df <- df[order(df$Freq, decreasing=TRUE),] # Sort in decreasing order
    rownames(df) <- NULL # Reset row names after re-ordering table
    if (nrow(df) > n) { # If nrow > n, summarize all values from n to nrows
        oc <- nrow(df) - n # Unique count of other elements
        on <- sum(df[-(1:n),]$Freq) # Total count of other elements
        df[(n+1),] <- list(paste0("Other (",oc,")"), on)
        df <- df[1:(n+1),]
        rownames(df)[n+1] <- "-"
    }
    df$Pct <- df$Freq/sum(df$Freq)*100 # Percentage
    df$Cmlpct <- round(cumsum(df$Pct),1) # Cumulative percentage
    df$Pct <- round(df$Pct,1) # Round to 1 d.p. for display
    return(df)
}

top <- topn(df$country,label="Country",n=10)
knitr::kable(top,row.names=TRUE)
```
